---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Kelly Arndt"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows 3 columns.
Variables: dataset, x-values, and y-values.

### Exercise 2

Plots data into dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculates correlation between `x` and `y` in dino dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

plots data into star dataset:

```{r plot-star, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculates correlation between `x` and `y` in star dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

Both r values show that the dino and star datasets have moderately strong, negative association with the star r value, -0.0629, being just a tad bit smaller than the dino r value, -0.0644.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)