---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Kelly Arndt"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows 3 columns.
Variables: dataset, x-values, and y-values.

### Exercise 2

Plots data into dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculates correlation between `x` and `y` in dino dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

plots data into star dataset:

```{r plot-star, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculates correlation between `x` and `y` in star dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

Both r-values show that the dino and star datasets have weak, negative association 
with the star r-value, -0.0629, being just a tad bit weaker than the dino r-value, 
-0.0644.

### Exercise 4

plots data into circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculates correlation between `x` and `y` in circle dataset:

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))
```

Both r-values show a weak, negative association for the datasets of dino and circle. 
The association of the circle dataset, -0.0683 however is slightly stronger than that 
of dino, -0.0644.

### Exercise 5


- Plots all 13 datasets giving each their own color, color = dataset, for data points. 
- Puts the plots into 3 columns, ncol = 3.
- Allows us to see all datasets, facet_wrap.
- Takes away a legend for datasets with corresponding color, theme(legend.position = "none").

```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) + 
  theme(legend.position = "none")
```

Calculates and displays r-values for all 13 datasets individually.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
